\documentclass[11pt, a4paper]{article}
\begin{document}
\title{Shifter}
\author{Jake Huxell\\
        Threetee Software}
\date{October 28th 2015}
\maketitle 
\newpage
\tableofcontents
\newpage
\section{Background}
On October 24th 2015 Hack Manchester began, where a gaggle of exceptionally bonkers programmers decided to spend the next 25 of their precious hours slamming raw concepts onto their keyboards and into the computer screen. The clock span, driving some groups into a frenzied exit as their ideas failed to dust off the cutting floor. Luckily, well lucky depends on perspective I guess, The Turgid Trumpets managed to hang on. That was the team I was part of.
Over the marathon we ended up making something truly, horrific, maddening and kind of alright I guess. Two people initially worked on the project, myself and my good chum Samuel Hodgkinson. He has since sort of drifted away from working on the project so it's mostly me responsible for this build currently. Even after the hackathon it took me 3 solid days to get the blasted thing building into a playable copy outside the engine!

\section{What Is Shifter As A Concept?}
Originally dubbed as "Carwaii" by yours truly, the decidedly awful nature of that name has given me recourse to change it to the slighly more moderate "Shifter". Cars have gearsticks and you play a world changing role, it's not super complex but it gets the general point home. 
The idea behind Shiter was to have a go at making a visual novel that sought to right the wrongs of the Hatoful Boyfriend game that recently awashed on steam somehow. It would be a visual novel with meaningful choices, enjoyable writing and proper character development. Unfortunately the contest wasn't a 2 month hackathon so we settled for laying down the foundations.
Essentially Shifter is a quirky visual novel game that will aim to use its frankly ludicrous premise to subvert expectations from its juxtapositionally organic characters and the world they inhabit. 
Lists make things like this easier to understand, so here's one you lazy goit. 
The game was made in The Ren'py engine, which is rather irritable and difficult to integrate a bunch of the time. It was written in Python and does support standard Python code though so there's room to build it. You just need to be gentle. 
\begin{enumerate}
\item{\textbf{Silly Premise - }Sets up user for shallow one note gag experience that completely twists them down a whole different rabbit hole.}
\item{\textbf{Strong Characters - }Make them strong, make them likeable. Keep the cast small but varied. Have a lot of chemistry between the major plot ones.}
\item{\textbf{Plentiful World Building - }Immerse people in this ludicrous world that Lightning McQueen might just try and sue us for. An example of this in the current build is the TV. It's a fun way to both add some user interaction and cheap laughs whilst also establishing the functionalities outside the player.}
\item{\textbf{Meaningful Impact - }Make characters hurt, cry and die. Make the player cause this and pile the bad times on them. Don't promise consequence, enforce it.}
\item{\textbf{Gameplay That Isn't Bollocks - }The gameplay should supercede dialogue choices. Have ones under a time pressure, or perhaps a chase/race scene. Mix it up a bit so the storytelling vehicle doesn't get stale.}
\item{\textbf{Investigative Storytelling - } Dialogue trees will live up to their namesake, and instead of being a start to finish list each option will have the potential to end the conersation right there. Think like L.A. Noire, you have to pick the right response for the right situation or be penalised.}
\item{\textbf{Offer No Dating - }The joke is you can't actually date a single one of these cars. If you could then this would cease to be a parody of the genre and instead sink into its grimy depths.}
\end{enumerate} 

These sum up the main points, in my mind, of what make Shifter what it is. And what it is spells doom for all involved.

\section{What Is Shifter Right Now?}
The current version only has the first day implemented with placeholder sounds and characters. The graphics and sounds will remain placeholders until the whole game has been written and programmed.

The branching dialogue trees have sort of been implemented but have a lot of room to grow. The main characters have been well established but some of the quirky crap needs a lot of cutting down in my opinion. 

The clockwork messaging API is included which lets in game characters text you as you play. I plan to keep this a thing for as long as I can, mainly because it was such a arsewipe to get working with Ren'py. 

However the structure of the first day and how it pans out is largerly complete at this point. 

\section{What I Hope It Will Become}
The current build is going to largerly be the final one for a good while now I imagine, as I'm not particularly interested in continuing the project \textbf{right now, but I hope to come back to it later down the road!}
Some planned stuff in the works will be listed here.
\begin{enumerate}
\item{Car racing mechanics.}
\item{Time sensitive choices.}
\item{Fully voice acted.}
\item{Meaningful depth to the mechanics}
\item{No dating. Never. Stop asking.}
\end{enumerate}
\end{document}


